Rust for Scientific Computing

### 2025-09-15 paper/main.tex
fix typo

As the preceding exmamples show, even a single programming language can span across multiple
abstraction levels, ranging from low-levels of operation to high-level ones.
The former mostly deal with instructions on a level close to the actual hardware such as memory
allocation, pointer arithmetic or by using assembly instructions directly.
Meanwhile, high-level operations usually combine many lower-level ones to perform a single task.
An example for a high-level operation would be the addition of two matrices which might allocate the
required memory, fill it according to the given values and then call the appropriate math function
to pairwise add their entries.
Languages which can operate effectively on a lower level often bear the most promise for maximum
performance which is crucial in any scientific application.
Of these languages almost all are compiled using an optimizing compiler which enables many of their
performance achievements.

>>>>

As the preceding examples show, even a single programming language can span across multiple
abstraction levels, ranging from low-levels of operation to high-level ones.
The former mostly deal with instructions on a level close to the actual hardware such as memory
allocation, pointer arithmetic or by using assembly instructions directly.
Meanwhile, high-level operations usually combine many lower-level ones to perform a single task.
An example for a high-level operation would be the addition of two matrices which might allocate the
required memory, fill it according to the given values and then call the appropriate math function
to pairwise add their entries.
Languages which can operate effectively on a lower level often bear the most promise for maximum
performance which is crucial in any scientific application.
Of these languages almost all are compiled using an optimizing compiler which enables many of their
performance achievements.
